### 2018-07-29 Sections/cloud_quantum_computing.tex
Modules fig

We envisage that physically, a module is a black box with optical interconnects, that may be interconnected to form an arbitrary topology. The user remains oblivious to the inner workings of the modules. The modules could all be identical, just patched together differently, paving the way for their mass production, and an associated quantum equivalent of Moore's Law, allowing them to become off-the-shelf commodity items over time. Then the cost of a quantum computer would simply scale linearly with its number of qubits.

>>>>

We envisage that physically, a module is a black box with optical interconnects, that may be interconnected to form an arbitrary topology, yielding a physical platform as shown in Fig.~\ref{fig:modules_physical}. The user remains oblivious to the inner workings of the modules. The modules could all be identical, just patched together differently, paving the way for their mass production, and an associated quantum equivalent of Moore's Law, allowing them to become off-the-shelf commodity items over time. Then the cost of a quantum computer would simply scale linearly with its number of qubits.

\begin{figure}[!htb]
	\includegraphics[width=0.475\textwidth]{modules_physical}
	\caption{A possible physical realisation of commercially produced quantum modules. Each hosts a relatively small number of qubits. The nodes each have four optical interconnects, which are used to connect the modules via optical fibre. Entangling operations performed on photons shared via the interconnects create inter-module entanglement, yielding a virtual quantum computer with far more qubits.}\label{fig:modules_physical}
\end{figure}
